
\documentclass{resume} 
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} 
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\input{glyphtounicode}
\pdfgentounicode=1


\name{Nigel Dsilva} % Your name
\address{Dubai, United Arab Emirates} 
\address{(+971)545334486 \\ nigel333dsilva@gmail.com \\ linkedin.com/in/nigeldsilva4}
\begin{document}

\begin{rSection}{Career Objective}
    To work for an organization which provides me the opportunity to improve my skills and knowledge to grow along with the organization objective.
\end{rSection}

\begin{rSection}{Work Experience}
    \begin{rSubsection}{Blue Logic Digital, Dubai}{July 2021 - Present}{Junior Front End Developer}{}
        \item Implemented responsive websites and landing pages from concept through deployment.
        \\ \emph{Eg: Reem Hospitals, Aster, Medcare, Aramed, Centric Compounding.}
        \item Implemented UX and UI designs on top of themes for Magento based E-commerce websites.
        \\ \emph{Eg: Aster Otpicals, Novo Pharmacy.}
        \item Assessed UX and UI designs for technical feasibility. 
        \item Collaborated with product team members to implement new feature developments.
        \item Developed on top of existing Chat Bot templates using ReactJS. 
        \\ \emph{Eg: Reem Hospitals}
    \end{rSubsection}

\end{rSection}

\begin{rSection}{Education}

    {\bf Heriot-Watt University} \hfill {\em September 2017 - April 2021}
    \\ Honours Degree, Bachelor of Sciences, Computer Science.\hfill { Overall GPA: 3.5/4 }

\end{rSection}

\begin{rSection}{Technical Strengths}

    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
        Languages \        & Python, Javascript    \\
        Technologies       & HTML5, CSS, ReactJS      \\
        Tools              & Visual Studio Code       \\
        % Databases          & MySql, Oracle, Sqlite, NoSql \\
        % Cloud Technologies & Firebase, AWS, Google Cloud  \\
        Version Control    & Github
    \end{tabular}

\end{rSection}

\begin{rSection}{Languages}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
        English: \    & Native Proficency    \\
        Konkani:      & Native Proficency      \\
        
    \end{tabular}
\end{rSection}

\begin{rSection}{Noteable projects}
    {\bf Future Home System - III Full Year Project}
    \\Implementation of MQTT, Django, Flutter, and Python.
    Designed a smart home system that monitors energy usage and where switches can be
    controlled from a device with an internet connection. (Group 3rd year project)

    {\bf REF2014 Dashboard - IV Year}
    \\Implementation of D3.JS.
    Designed a dashboard for the Visualization of data provided in REF2014 dataset.

    {\bf A Statistical study of COVID-19 - Final Year Project}
    \\Implementation of Pandas, PyPlot, SciPy, and NumPy.
    A dissertation studying the efficiency of a SIR Model relating to COVID-19 and
    parameters that affect the Beta and Gamma values for COVID-19.
\end{rSection}
% 
% 
% \newpage

% 
\newpage


\begin{rSection}{Extra-Cirrucular}
    \item Attended a workshop on Machine Learning and artificial intelligence from faculties of IIT Roorkee in 2019 and won zonal round for the challenge presented.
    \item Member of the  Institute of Engineers since 2017.
    \item Completed Basic Leadership Training under Project NSS, Gujarat
    \item Attended a workshop on Machine Learning and artificial intelligence from faculties of IIT Roorkee in 2019 and won zonal round for the challenge presented.
    \item Member of the  Institute of Engineers since 2017.
    \item Completed Basic Leadership Training under Project NSS, Gujarat
    \item Attended a workshop on Machine Learning and artificial intelligence from faculties of IIT Roorkee in 2019 and won zonal round for the challenge presented.
    \item Member of the  Institute of Engineers since 2017.
    \item Completed Basic Leadership Training under Project NSS, Gujarat

\end{rSection}






\end{document}
